% Autogenerated translation of research.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\hrule
layout: archive
title: "Research"
permalink: /research/

\section*{author\_profile: true}

\section*{Working papers}

\section*{Publications}

\begin{itemize}
\item \textbf{Mozer, R.}, Miratrix, L., Relyea, J. E., and Kim, J. S. (2023). \href{https://journals.sagepub.com/doi/full/10.3102/10769986231207886}{Combining human and automated scoring methods in experimental assessments of writing: A case study tutorial.} \emph{Journal of Educational and Behavioral Statistics}
: \href{https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/J9KSHU}{[data]}
\item \textbf{Mozer, R.} and Glickman, M. E. (2023). \href{https://link.springer.com/article/10.1007/s10742-022-00295-7}{Bayesian analysis of longitudinal studies with treatment by indication.} \emph{Health Services and Outcomes Research Methodology}, 23(4):468--491\texttt{$<$br$>$}
    ~~~~Link, Code
\item Anderson, E., Dvorin, K., Etingen, B., Barker, A. M., Rai, Z., Herbst, A. N., \textbf{Mozer, R.}, Kingston, R. P., and Bokhour, B. G. (2022). \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/hex.13581}{"It Makes You Sit Back and Think Where You Wanna Go": Veteran experiences in virtual whole health peer-led groups.} \emph{Health Expectations}, 25(5):2548--2556
: Link \texttt{$<$img src="../images/github-mark.png" width="20" height="20"$>$}
\item Rahman, N., \textbf{Mozer, R.}, McHugh, R. K., Rockett, I. R., Chow, C. M., and Vaughan, G. (2022). \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/sltb.12862}{Using natural language processing to improve suicide classification requires consideration of race.} \emph{Suicide and Life Threatening Behavior}, 52(4):782--791
\item Anderson, E., Dvorin, K., Barker, A., Herbst, A., Bowen, M., Etingen, B., \textbf{Mozer, R.}, Kingston, R., and Bokhour, B. (2022). Lessons learned from VHAs rapid implementation of virtual whole health peer--led groups during the COVID--19 pandemic: Staff perspectives. \emph{Global Advances in Health and Medicine}, 11:1--12
\item \textbf{Mozer, R.}, Miratrix, L., Kaufman, A. R., and Anastasopoulos, L. J. (2020). Matching with text data: An experimental evaluation of methods for matching documents and of measuring match quality. \emph{Political Analysis}, 28(4):445--468
\item \textbf{Mozer, R.}, Rubin, D. B., and Zubizarreta, J. R. (2020). Statistical inference for causal effects in clinical psychology: Fundamental concepts and analytical approaches. In Wright, A. C. and Halquist, M. N., editors, \emph{The Cambridge Handbook of Research Methods in Clinical Psychology}, chapter 31, pages 415--425. Cambridge University Press, Cambridge, UK
\item Bavli, H. J. and \textbf{Mozer, R.} (2019). The effects of comparable-case guidance on awards for pain and suffering and punitive damages: Evidence from a randomized controlled trial. \emph{Yale Law and Policy Review}, 37(405)
\item Kessels, R., \textbf{Mozer, R.}, and Bloemers, J. (2019). Methods for assessing and controlling placebo effects. \emph{Statistical Methods in Medical Research}, 28(4):1141--1156
\item \textbf{Mozer, R.}, Kessels, R., and Rubin, D. B. (2017). Disentangling treatment and placebo effects in randomized experiments using principal stratification: an introduction. In \emph{The Annual Meeting of the Psychometric Society}, pages 11--23. Springer
\end{itemize}

\end{document}
